---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# teivents

<!-- badges: start -->
<!-- badges: end -->

Utility functions for importing events in tracker program.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("INyabuto/teivents")
```
## Example

This is a basic example which shows you how to generate an event payload from event line list:

```{r example}
library(teivents)
## generate event payload
sample_events <- teivents::tei_events

event_payload <- generate_tei_events_payload(sample_events)

# as json
d <- jsonlite::toJSON(list(events = event_payload), auto_unbox = T, pretty = T)

d

```

You can save the json payload to disk and send to the `events endpoint` using curl as described on the [DHIS2 guide](https://docs.dhis2.org/en/develop/using-the-api/dhis-core-version-master/tracker.html) or upload the events directly with `create_events` as follows: 

```{r}

#d <- create_events(sample_events)

```

this will generate the payload and uplaod to the events endpoint using `httr` package.

Be sure to first set the config params in your `r_environ` or you could pass them directly in the function call as follows: 

```{r}
# d <- create_events(sample_events, 
#                    baseurl = "https://play.dhis2.org/2.33nightly/",
#                    user = "admin",
#                    pass = "district"
#                    )
```

or by including the config in the `r_environ`: 

```{r}
usethis::edit_r_environ()
```

the following is a sample config: 

```r

C_USER = "admin" # dhis2 account
C_PASS = "district" # dhis2 pass 
BASEURL = "https://play.dhis2.org/2.33nightly/" # the server url
USER_AGENT = "https://github.com/INyabuto/teivents"

```
